---
title: "Add descriptive title here"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Add descriptive title here}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

*Give short (1 paragraph) overview of vignette, e.g., This vignette
demonstrates how to use the function `prcomp` to compute principal
components of a data set (the Iris data), and gives an example of a
plot that can easily be created from the PCA results.*

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = TRUE,comment = "#",fig.width = 5,
                      fig.height = 4,fig.align = "center",
                      fig.cap = "&nbsp;")
```

Begin by loading these packages into your R environment. 

```{r, message = FALSE}
library(stats)
library(EbayesThresh)
```

## Load the data

Load the Iris data.

```{r}
data(iris)
```

Compute principal components using `prcomp`.

```{r}
out.pca <- prcomp(iris[1:4])
```

## Create visualizations of the Iris PCA results

```{r}
plot(out.pca,type = "lines")
```

